Example of Market Simulator Dasbhaord

### 2021-09-22 README.Rmd
Also ignore _targets

If you're part of the research team and using Dropbox, make sure you make it so that Dropbox ignores the `posterior_draws` folder. There are [complete instructions for doing that here](https://help.dropbox.com/files-folders/restore-delete/ignored-files). In short, run one of these commands in your terminal:

```sh
# On macOS
cd path/to/this/project
xattr -w com.dropbox.ignored 1 data/raw_data/posterior_draws

# On Windows (with PowerShell)
cd path/to/this/project
Set-Content -Path 'data/raw_data/posterior_draws' -Stream com.dropbox.ignored -Value 1
```

>>>>

### Ignoring things in Dropbox

If you're part of the research team and using Dropbox, make sure you make it so that Dropbox ignores the `posterior_draws` folder and the `_targets` folder. There are [complete instructions for doing that here](https://help.dropbox.com/files-folders/restore-delete/ignored-files). In short, run one of these commands in your terminal:

```sh
# On macOS
cd path/to/this/project  # Not needed if you use the terminal panel in RStudio after opening the project
xattr -w com.dropbox.ignored 1 _targets
xattr -w com.dropbox.ignored 1 data/raw_data/posterior_draws

# On Windows (with PowerShell)
cd path/to/this/project  # Not needed if you use the terminal panel in RStudio after opening the project
Set-Content -Path '_targets' -Stream com.dropbox.ignored -Value 1
Set-Content -Path 'data/raw_data/posterior_draws' -Stream com.dropbox.ignored -Value 1
```
